\documentclass[10pt]{homework}

\newcommand{\hwname}{Carter Larsen}
\newcommand{\hwemail}{clars32@byu.edu}
\newcommand{\hwtype}{Group Project Proposal}
\newcommand{\hwnum}{}
\newcommand{\hwclass}{CS 270}
\newcommand{\hwsection}{$($Sec. $001)$}

\usepackage{multicol}

\begin{document}
\maketitle

\begin{center}
    "Predicting Weekly Fantasy Football Scoring Output" \\
    My Interest Level: 10/10
\end{center}

\question*{Description}

Fantasy football is a popular game that allows competitors to assemble their own virtual team
of real-life NFL players. These players earn points for their team based off of their real-life
performance (e.g. 4 points per passing TD, 1 point for every 10 rushing yards, etc.).
Teams are matched up against each other, and whichever team finishes with the higher 
total score is said to have won the matchup that week. This continues over the course of a season
until a league champion (and league loser) is crowned.

This project aims to use machine learning to predict the fantasy score of an NFL
player on a given week. Using the wealth of data publicly available both as actual NFL stats
and expert predictions specific to fantasy football, the model will aim to use past performance
and current projections to create a reasonable estimate for the fantasy score of the player.

\question*{Possible Features}

Some possible features the model could include are:

\begin{multicols}{2}
    \begin{itemize}
        \item Fantasy points scored the previous week/3 weeks/season/etc.
        \item Expert projected points for that week
        \item Average points scored the previous season
        \item Average points given up to the player's position by the opposing defense
        \item If the player is playing at home or away
        \item Individual rushing/passing yards, touchdowns, etc. instead of total points
    \end{itemize}
\end{multicols}

Here is what an example of an instance could look like:

\begin{center}
    \begin{tabular}{ccccccc}
        SeasonAvgPts & Last3WeeksAvg & LastWeekPts & ExpertProj & Home/Away & Target: Fantasy Points \\
        \hline
        14.445 & 15.04 & 13.24 & 15.37 & A & 8.40
    \end{tabular}
\end{center}

\question*{Gathering Data}

Data for both player stats and fantasy projections is widely available. For example, pro-football-reference.com
has the complete game log for all NFL players, including all stats (features for the model) and fantasy points
scored (the targets for the dataset). fantasydata.com provides a multitude of player projections, including
historical data that can be used in training. The main task in gathering and labeling data would be to scrape
the data from the different sources, combine it all into a usable dataset, clean it, and normalize it for use.
Dataset size should not be a problem as data exists for the top players over the last several years.

\end{document}
